---
title: "Group 40 CA pollution burden"
author: "Renee LaManna & Jaxon Stuhr"
date: "11/15/2021"
output: html_document
---

## Setup

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(janitor)
library(here)
```

## Read in data

```{r}
# read in data and clean names
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r}
# ggplot percent white vs pollution burden
ggplot(ces, aes(x = white_percent, y = ces_3_0_score)) + 
  # hex bin
  geom_hex() +
  # define low, high colors
  scale_fill_gradient(low = "green", high = "red") + 
  # add labels
  labs(x = "% white population",
       y = "CalEnviroScreen 3.0 score") +
  # update theme
  theme_minimal()  


```

**Figure 1.** CalEnviroScreen 3.0 score which combines both pollution burden and population characteristics for an aggregate score for a given % white population. 


## Summary and Analysis:

The primary trend we see in this data is that as the percent of the population that is white increases, the CalEnviroScreen 3.0 score decreases, meaning the environmental burden is smaller in whiter areas.

## Data Citation:

OEHHA. CalEnviroScreen 3.0. 2017. https://oehha.ca.gov/calenviroscreen/report/calenviroscreen-30. Accessed 7 Jun 2017.

Testing commits...


